Response to reviewers

### 2024-11-29 Manuscript/ecography_reponse_letter.tex
reviewer 2 done

Additionally, there appears to be a logical inconsistency.
% Figure 2 illustrates the difference between two functional diversity metrics, rather than the metrics themselves
% Therefore, changes in this difference do not provide information about the individual increases or decreases of the metrics.
%  We have now added supplementary figures showing the scaled metric score changes (to keep the values manageable between 0 and 1) but not also scaled to the null mechanism changes (to display just the raw metric changes).

\textcolor{blue}{L 287: Why would this be ``unexpected''?}
%  We removed the word ``unexpected'' that was maybe ironic (and irrelevant regardless).

\textcolor{blue}{LL 287-289: I do not see that the ``what, how, why''-framework has really been used in this study.
Please specify, for example, which mechanisms have correctly been explained in the analysis?}
%  We have now reworked this section with the inclusion of a Box explaining in more details how we believe that using the ``what, how, why'' framework helps choosing the correct metric for a specific dataset and question.

>>>>

\textcolor{blue}{Additionally, there appears to be a logical inconsistency.
Figure 2 illustrates the difference between two functional diversity metrics, rather than the metrics themselves.
Therefore, changes in this difference do not provide information about the individual increases or decreases of the metrics.}

We have now added supplementary figures 3, 4 and 5 showing the scaled metric score changes (to keep the values manageable between 0 and 1) but not also scaled to the null mechanism changes (to display just the raw metric changes).

\textcolor{blue}{L 287: Why would this be ``unexpected''?}

We removed the word ``unexpected'' that was maybe ironic (and irrelevant regardless).

\textcolor{blue}{LL 287-289: I do not see that the ``what, how, why''-framework has really been used in this study.
Please specify, for example, which mechanisms have correctly been explained in the analysis?}

We have now reworked this section with the inclusion of a Box explaining in more details how we believe that using the ``what, how, why'' framework helps choosing the correct metric for a specific dataset and question.
